---
title: "Clamp Exploration - Run007"
output: 
  html_document:
    toc: true
    toc_float: true

---

```{r setup, include=FALSE}
library(knitr)
library(pheatmap)
library(data.table)
library(tidyverse)
library(viridis)
library(RColorBrewer)

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
knitr::opts_chunk$set(error = FALSE)

```

Initial Clamp Probe Blast Analysis
---------------


```{r pressure, echo=FALSE,warning=FALSE,echo = FALSE}

counts = fread("D:/Work/Code/Clamp/counts.csv")
matrix = fread("C:/Users/danie/Downloads/clamp_blast_matrix (1).csv") %>% as.data.frame() %>% column_to_rownames("qseqid")
rc = fread("C:/Users/danie/Downloads/clamp_output_rc.csv")
key= fread("C:/Users/danie/Downloads/key_clamp.csv") %>% column_to_rownames("Name")
key2= fread("C:/Users/danie/Downloads/sequences (1).csv") %>% select(Accession,Location,Species_mini) %>% right_join(colnames(matrix) %>% as.data.frame() %>% rename(Accession = ".")) %>% filter(Location!="#N/A") %>% column_to_rownames("Accession")


# mat_colors_col = list(Location = cbind(unique(key2$Location),viridis(length((unique(key2$Location))))))

mat_colors_col2 <- list(Location = c(brewer.pal(9, "Paired")))
    names(mat_colors_col2$Location) <- unique(key2$Location)

xx = pheatmap(t(matrix),annotation_col = key,annotation_row = key2,show_rownames = F,show_colnames = F,
         cutree_cols = 4,annotation_names_row = T,main = "Clamp CV probes vs CV genomes",annotation_colors = mat_colors_col2,
         annotation_legend = T,fontsize = 7)

```

To better characterize the cross-reactivity amongst our clamp-seq CV probes, I performed a blastn search comparing the reverse complement of the 58 designed clamp probes against 565 coronavirus genomes and found 4828 probe - genome matches. Converting the resulting data into a matrix of clamp probes vs genomes, with ppos as the values within the cells, and clustering yields the above heatmap. I pulled some meta info on both the probes and the genomes, distinguishing whether probes were from the inital "general CV" pool or the substrain specific pull. I also pulled a meta column "Geo Location" that was associated with each CV genome.

As a note I did some manual pooling of countries to get a more managable list of Locations and pulled the species associated with each sequence.

## Header 2


```{r }
tmp = counts %>% filter(`fasta[, 1]` %in% rownames(matrix)) %>%  column_to_rownames("fasta[, 1]")
tmp_sub = tmp %>% select(tmp %>% colSums %>% as.data.frame() %>% rownames_to_column()%>%  filter(. >=10) %>% select(rowname) %>% unlist() %>% as.character())
tmp_sub = tmp_sub %>% rownames_to_column() %>% mutate(rowsum = rowSums(.[2:23]))
```




